A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-06-16 paper/poster.tex
start poster and add missing file

\definecolor{lightyellow}{cmyk}{0,0,0.3,0.0}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lightestyellow}{cmyk}{0,0,0.05,0.0}
\begin{poster}{
  % Show grid to help with alignment
  grid=yes,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lighteryellow,
  bgColorTwo=lightestyellow,
  borderColor=reddishyellow,
  headerColorOne=yellow,
  headerColorTwo=reddishyellow,
  headerFontColor=black,
  boxColorOne=lightyellow,
  boxColorTwo=lighteryellow,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=yes,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  { % No eye catcher for this poster. If an eye catcher is present,
    % the title is centered between eye-catcher and logo.
    \includegraphics[height=5.5em]{figs/osu-logo}
  }
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  A Classical Density Functional for Water}
  % Authors
  {\sf %Sans Serif
  % Serif
  David Roundy\hspace{3em}
  Jessica Hughes\hspace{3em}
  Oregon State University, USA
  }
  % University logo
  {
    \includegraphics[height=5.5em]{figs/osu-logo}
  }

@@

  \headerbox{Classical DFT}{name=cdft,column=0,row=0}{
    We will present preliminary results for a classical density
   functional for water based on the Statistical Associating Fluid
   Theory (SAFT), designed to be suitable for treatment of either
   solutes or the solid-liquid interface.  The functional is based on
   a combination of the Fundamental Measure Theory functional
   describing hard-sphere fluids with the SAFT-VR equation of state.
   We will present bulk thermodynamic results together with results on
   the hydrophobic interaction of planes, rods and spheres.  }

  \headerbox{Statistical Associating Fluid Teory}{name=saft,column=0,below=cdft}{
    Hello world
  }

  \headerbox{The
    Functional}{name=fitting,column=0,below=saft,above=bottom}{ We
    introduce a new classical density functional for water.  The
    Helmholtz free energy functional is based on SAFT, and is composed
    of the usual terms:
    \begin{equation}
      F[n] = F_\textit{id}[n] + F_\textit{hs}[n] + F_\textit{assoc}[n] + F_\textit{disp},
    \end{equation}
    We model the repulsive interactions using the White Bear version of
    the Fundamental-Measure Theory~(FMT) functional published in
    reference~\cite{roth2002whitebear}.
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Water Confined in a Slit}{name=1D,column=1,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{A Cylinder in Water}{name=rod,column=1,below=1D,span=1,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Two Cylinders in Water}{name=two rods,column=2,span=2,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{multicols}{2}
        This text will be in two separate columns.
        This text will be in two separate columns.
        This text will be in two separate columns.
        This text will be in two separate columns.
        This text will be in two separate columns.
        This text will be in two separate columns.
        This text will be in two separate columns.
      \end{multicols}\vspace{-1em}
      \mbox{\hspace{0.3\linewidth}\rule{0.4\linewidth}{1pt}\hspace{0.3\linewidth}}\\

>>>>

\definecolor{lightyellow}{cmyk}{0,0,0.3,0.0}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lightestyellow}{cmyk}{0,0,0.05,0.0}
\begin{poster}{
  % Show grid to help with alignment
  grid=yes,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lighteryellow,
  bgColorTwo=lightestyellow,
  borderColor=reddishyellow,
  headerColorOne=yellow,
  headerColorTwo=reddishyellow,
  headerFontColor=black,
  boxColorOne=lightyellow,
  boxColorTwo=lighteryellow,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=yes,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  { % No eye catcher for this poster. If an eye catcher is present,
    % the title is centered between eye-catcher and logo.
    \includegraphics[height=5.5em]{figs/cavitysize-060}
  }
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  A Classical Density Functional for Water}
  % Authors
  {\sf %Sans Serif
  % Serif
  David Roundy\hspace{3em}
  Jessica Hughes\hspace{3em}
  Oregon State University, USA
  }
  % University logo
  {
    \includegraphics[height=5.5em]{figs/osu-logo}
  }

@@

  \headerbox{Classical DFT}{name=cdft,column=0,row=0}{ Classical
    Density-Functional Theory is a continuum empirical approach to
    modelling fluid behavior when the density is inhomogeneous---as is
    the case at interfaces.  We have developed a classical density
    functional for water, which provides a description of hydrophobic
    interactions.  }

  \headerbox{Statistical Associating Fluid
    Teory}{name=saft,column=0,below=cdft}{ The statistical associating
    fluid theory (SAFT) is a well-established approach for the
    description of the thermodynamics and phase equilibria of fluid
    systems, with particular applicability to hydrogen-bonding fluids.
    Our functional reduces in the homogeneous limit to the SAFT model
    for water developed in reference~\cite{clark2006developing}.
    \begin{center}
      \includegraphics[width=\columnwidth]{figs/pressure-with-isotherms}
    \end{center}
    This functional accurately describes the liquid-vapor phase
    diagram away from the critical point, but gives a poor description
    of the compressibility.
  }

  \headerbox{The
    Functional}{name=fitting,column=0,below=saft,above=bottom}{ We
    introduce a new classical density functional for water.  The
    Helmholtz free energy functional is based on SAFT, and is composed
    of the usual terms:
    \begin{equation}
      F[n] = F_\textit{id}[n] + F_\textit{hs}[n] + F_\textit{assoc}[n] + F_\textit{disp},
    \end{equation}
    We model the repulsive interactions using the White Bear version
    of the Fundamental-Measure Theory~(FMT)
    functional~\cite{roth2002whitebear}.  The association term is
    taken from~\cite{yu2002fmt-dft-inhomogeneous-associating}, and we
    used a simple and efficient functional for the dispersion
    interaction with a single tunable parameter.
  }

  \headerbox{Surface Tension}{name=1D,column=1,row=0}{

  }
  \headerbox{A Cylinder in Water}{name=rod,column=1,below=1D,span=1,above=bottom}{
    \begin{center}
      \includegraphics[width=\columnwidth]{figs/density-vs-radius}
    \end{center}
    \begin{center}
      \includegraphics[width=\columnwidth]{figs/energy-vs-diameter}
    \end{center}
  }
  \headerbox{Two Cylinders in Water}{name=two rods,column=2,span=2,row=0}{
    \begin{multicols}{2}
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
      This text will be in two separate columns.
    \end{multicols}\vspace{-1em}
    \begin{center}
      \includegraphics[width=0.45\columnwidth]{figs/density-rods-in-water}
      \hspace{1em}
      \includegraphics[width=0.45\columnwidth]{figs/density-rods-in-water}
    \end{center}
